\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-07 Papers/ViscousInstabilities/article_figure1.tex
do not rush kostas

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_100.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{10.0cm} (a)     
}
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_490.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{10.cm} (b)      
}
}     
\caption{ contours of Darcy velocity in XY and YZ planes for (a) t=$$s and (b)t=$$s.}
\label{fig:3DChannel_darcy_vel}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_100.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{10.0cm} (a)     
}
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{10.cm} (b)      
}
}     
\caption{For the same time steps as in Figure \ref{fig:3DChannel_darcy_vel} there is a description of the saturation front in (a) t=$$s and (b)t=$$s.}
\label{fig:3DChannel_sat}
\end{figure}
\end{landscape}
\clearpage

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_100.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{10.0cm} (a)     
}
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_490.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{10.cm} (b)      
}
}     
\caption{ contours of Darcy velocity in XY and YZ planes for (a) t=$0.91$s and (b)t=$4.3$s.}
\label{fig:3DChannel_darcy_vel}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_100.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{10.0cm} (a)     
}
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{10.cm} (b)      
}
}     
\caption{For the same time steps as in fig.\ref{fig:3DChannel_darcy_vel} there is a description of the saturation front in (a) t=$0.91$s and (b)t=$4.3$s.}
\label{fig:3DChannel_sat}
\end{figure}
\end{landscape}
\clearpage
